Sound Automated Synthesis of Digital Controllers

### 2016-10-12 paper/paper.tex
some fixes on AAs comments

\begin{mylemma}{\cite{Bessa16,fadali}}
\label{lemma:eq_int_stab} 
A feedback hybrid control system as shown in Fig.~\ref{fig:sampledsystem}, with a FWL implementation of the digital controller $\hat{C}(z) = \frac{FWL[N_{C}(z)]}{FWL[D_{C}(z)]}$ and uncertain discrete model of the plant $\hat{G}(z)=G(z)+\Delta G_{P}(z)=\frac{\hat{N}_{G}(z)}{\hat{D}_{G}(z)}$, is BIBO-stable if and only if: 
\red{[this statement does not seem to encompass the quantisation effects on the plant?]} 
\begin{itemize}
\item  the roots of characteristic polynomial $S(z)$ are inside the open unit circle, where $S(z)$ is:
\begin{equation}
\label{eq:internal_stab_lemma}
S(z)=FWL[N_{C}(z)]\hat{N}_{G}(z)+FWL[D_{C}(z)]\hat{D}_{G}(z);
\end{equation}
\item the direct loop product $\frac{FWL[N_{C}(z)]}{FWL[D_{C}(z)]}\cdot \frac{\hat{N}_{G}(z)}{\hat{D}_{G}(z)}$ has no pole-zero cancellation on or outside the unit circle.
\end{itemize}
\end{mylemma}

@@

\red{[first: lemmae precede theorems. \\
second: bounded is not energy bounded. ]}

%
\begin{myassumption}
\label{whitenoise}
%
The quantisation noises $\nu_{1}$ (from the $Q1$) and $\nu_{2}$ (from the
$Q2$) are energy bounded uncorrelated white noises.
% 
\end{myassumption}

>>>>

\begin{mylemma}{\cite{Bessa16,fadali}}
\label{lemma:eq_int_stab} 
A feedback hybrid control system as shown in Fig.~\ref{fig:sampledsystem}, with a FWL implementation of the digital controller $\hat{C}(z) = \frac{FWL[N_{C}(z)]}{FWL[D_{C}(z)]}$ and uncertain discrete model of the plant $\hat{G}(z)=G(z)+\Delta G_{P}(z)+\Delta G_{Q}(z)=\frac{\hat{N}_{G}(z)}{\hat{D}_{G}(z)}$, is BIBO-stable if and only if: 
\begin{itemize}
\item  the roots of characteristic polynomial $S(z)$ are inside the open unit circle, where $S(z)$ is:
\begin{equation}
\label{eq:internal_stab_lemma}
S(z)=FWL[N_{C}(z)]\hat{N}_{G}(z)+FWL[D_{C}(z)]\hat{D}_{G}(z);
\end{equation}
\item the direct loop product $\frac{FWL[N_{C}(z)]}{FWL[D_{C}(z)]}\cdot \frac{\hat{N}_{G}(z)}{\hat{D}_{G}(z)}$ has no pole-zero cancellation on or outside the unit circle.
\end{itemize}
\end{mylemma}

@@

\red{[first: lemmae precede theorems. ]}

%
\begin{myassumption}
\label{whitenoise}
%
The quantisation noises $\nu_{1}$ (from the $Q1$) and $\nu_{2}$ (from the
$Q2$) are bounded uncorrelated white noises.
% 
\end{myassumption}
